Visualizing Independence Using Extended Association and Mosaic Plots

### 2003-07-08 trunk/vcd/paper/draft.Rnw
made changes necessary for the package, vignette and papers to pass R CMD check; vignette should probably be removed for release
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@273 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[10pt]{article}
\usepackage{Sweave, graphicx}
\usepackage{Z}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(t(goals), main = NULL)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(t(haireye), main = NULL)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data (female students).}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
##grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
grid.mosaicpairs(UCBAdmissions, type = "conditional", permute = FALSE)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}

>>>>

\documentclass[10pt]{article}
\usepackage{Z}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(goals, main = NULL, gp = gp.HCLshading)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(haireye, main = NULL, gp = gp.HCLshading)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data (female students).}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
##grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
grid.mosaicpairs(UCBAdmissions, type = "conditional", permute = FALSE, gp = gp.HCLshading)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}
